Evaluating the evidence of widespread maintenance of functional composition in vertebrate communities

### 2021-09-30 paper/manuscript.Rmd
clean up

What does local maintenance of functional structure mean for the function of these communities?
The vast majority of experimental and observational work links function to changes in functional or species diversity.
By those criteria, very few observed communities in our dataset are in a state of concern for declining functionality.
However, we did not we did not directly measure some aspects of community structure important for ecosystem multifunctionality [e.g. dispersion, rarity, abundance of dominant species; @bagousse-pinguet2021].
While our metrics indirectly incorporate dimensions of the functional space related to those characteristics, they are likely not sensitive enough to infer deterioration (or improvement) in those those aspects of structure.

<!-- has important implications for biodiversity and ecosystem function (BEF). BEF work links ecosystem function to changes in species and functional diversity, however very few observed communities experienced changes along either of those characteristics. Do we then not need to worry about loss of function in most bird, mammal and amphibian communities? While -->

<!-- Always the option that we didn't measure traits related to function, though in this case I think we did. We did not however measure fucntional redundancy, which could be important for maintaining multifunctionality [@bagousse-pinguet2019] . Also may not be sensitive enough to detect significant decreases in abundance for the most dominant species, which may also be important-->

<!-- meet the criteria for biodiversity loss as defined in BEF work (loss of species or loss of functional diversity) and the communities that lost species maintained functional diversity. Need to measure the right traits, but also decide what kind of shifts are important for functional change. But this is also good news! Most communities appear to be just fine from a function standpoint following best practices. -->

@@

any differences in some of the taxonomic groups even if not significant?

do we expect different results for different taxa?

<!-- how does this reconcile with the large body of studies showing that extinctions primarily affect functionally rare species? It seems inconsistent with their findings -->

Maintenance of functional composition contradicts likely scenarios of loss predicted due to rare species extinction.
Rare species, defined by small populations and geographic restriction, are simultaneously more likely to be functionally distinct and at higher risk for extinction [@davies2004; @harnik2012; @loiseau2020].
Assuming local extirpation is a precursor to global extinction, communities losing functionally rare species should exhibit strong functional shifts as lost species cannot be replaced by functionally similar species [@leitão2016] .
Instead, these communities appear to only have turnover of species with functionally redundant species in the species pool.
<!-- good news for ecosystem function! -->

>>>>

What does local maintenance of functional structure mean for the function of these communities?
The vast majority of experimental and observational work links function to changes in functional or species diversity.
By those criteria, very few observed communities in our dataset are in a state of concern for declining functionality.
However, we did not we did not directly measure some aspects of community structure important for ecosystem multifunctionality [e.g. dispersion, rarity, abundance of dominant species; @bagousse-pinguet2021].
While our metrics indirectly incorporate dimensions of the functional space related to those characteristics, they are likely not sensitive enough to infer deterioration (or improvement) in those those aspects of structure.
<!-- more citations please -->

<!-- any work looking at function in communities that are stable along these axes? -->

While we did not directly measure changes in rare species, our results also contradict likely scenarios of loss predicted due to rare species extinction.
Rare species, defined by small populations and geographic restriction, are simultaneously more likely to be functionally distinct and at higher risk for extinction [@davies2004; @harnik2012; @loiseau2020]. Assuming local extirpation is a precursor to global extinction, communities losing functionally rare species should exhibit strong functional shifts as lost species cannot be replaced by functionally similar species [@leitão2016] .
Instead, these communities appear to only have turnover of species with functionally redundant species in the species pool.

@@
